Expanding the Popularity of the NHL Through Increased Goal Scoring

### 2023-04-18 outputs/paper/paper.qmd
model stuff

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

>>>>

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_1$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters. $\beta_1$ is teamwide shooting percentage, $\beta_2$ is teamwide powerplay percentage, $\beta_3$ is penalties drawn per 60.
